The hyper 2 package

### 2023-05-10 README.Rmd
typo

<!-- badges: start -->
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/freealg)](https://CRAN.R-project.org/package=freealg)
[![Build Status](https://travis-ci.org/RobinHankin/freealg.svg?branch=master)](https://travis-ci.org/RobinHankin/freealg)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/freealg)](https://cran.r-project.org/package=freealg)
<!-- badges: end -->

@@

For more detail, see the package vignette

`vignette("freealg")`

>>>>

<!-- badges: start -->
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/hyper2)](https://CRAN.R-project.org/package=hyper2)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/hyper2)](https://cran.r-project.org/package=hyper2)
<!-- badges: end -->

@@

For more detail, see the package vignette; type

`vignette("hyper2")`

at the R command line.
